Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-05-15 index.qmd
add questions
add uncounted slides

@@

2.

## How were NLP tasks hard before?

In your case when you use patent data, a lot of the research on historical questions is done just with the title of the patent and relationships between patent holders. It was difficult to get more information from the text of the patent.

@@

>>>>

## Vem är Karl Lund? {visibility="uncounted"}

@@

2. How should I classify the publications?
    - e.g. "Contemporary production of saw blades, circular saws, and machine knives" in the example of Karl Lund?

## How were NLP tasks hard before? {visibility="uncounted"}

In the case when you use patent data, a lot of the research on historical questions is done just with the title of the patent and relationships between patent holders. It was difficult to get more information from the text of the patent.

@@

## Tips for working with the OpenAI API {visibility="uncounted"}

### Ask for exactly what you want

"Structure the biography in Schema.org/Person format as a JSON object. Include dates wherever possible. Only provide a  RFC8259 compliant JSON response."

### Use GPT-4 to generate code to communicate with the API / visualize your data

"Great, thank you, Now I want to draw a map of these locations. What I want to do is create a dictionary with name, birthPlace (and coordinates) and jobTitle from the files in data/biographies_augmented, and then draw a map that I can export as jpeg. The map should have dots for birth place"
